gender and age in food incentive

### 2024-02-19 outputs/paper/paper.qmd
Updated simulate_data and test_data scripts
Updated graphs

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: tbl-table1
#| tbl-cap: ""

@@

# Create a bar plot
ggplot(food_choices, aes(x = as.factor(grade), fill = Switched)) +
  geom_bar(position = "dodge") +
  geom_text(
    aes(label = after_stat(count)),
    stat = "count",
    position = position_dodge(width = 0.9),
    vjust = -0.5, # Adjust the vertical position of the labels
    color = "black",
    size = 3
  ) +
  labs(title = "Students Food Choices From Stage G1 to G2",
       x = "Grade",
       y = "Number of Observations") +
  scale_fill_manual(values = c("Cookie to Grape" = '#BDBDBD',"Grape to Cookie" = '#757575', "Not Changed" = '#424242')) +
  scale_x_discrete(breaks = as.character(0:8)) +
  theme_minimal()

@@

# Create the bar graph
ggplot(proportions, aes(x = factor(free), y = Proportion, fill = factor(free))) +
  geom_bar(stat = "identity") +
  labs(title = "Incentivized Students Choosing Grapes, By Free Lunch Status",
       x = "Eligible for Free Lunch",
       y = "Proportion",
       fill = "Eligible for Free Lunch") +
  scale_fill_manual(values = c('#BDBDBD', '#424242'), labels = c("No", "Yes")) +
  scale_x_discrete(labels = c("0" = "No", "1" = "Yes")) +  # Adjust x-axis labels  
  scale_y_continuous(limits = c(0, 1)) +  # Set y-axis limits  
  theme_minimal()

@@

# Create the bar chart
ggplot(proportions_long, aes(x = grade, y = proportion, fill = choice)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Incentivized Students' Final Food Choice, By Grade",
       x = "Grade",
       y = "Proportion",
       fill = "Choice") +
  scale_fill_manual(values = c("grapes_proportion" = '#BDBDBD', "cookies_proportion" = '#424242'),
                    labels = c("Grapes", "Cookies")) +
  ylim(0,1) +
  theme_minimal()

@@

# Create the bar chart
ggplot(proportions_long, aes(x = male, y = proportion, fill = choice)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Incentivized Students' Final Food Choice, By Gender",
       x = "Gender",
       y = "Proportion",
       fill = "Choice") +
  scale_fill_manual(values = c("grapes_proportion" = '#BDBDBD', "cookies_proportion" = '#424242'),
                    labels = c("Grapes", "Cookies")) +
  ylim(0,1) +
  theme_minimal()

>>>>

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: tbl-table1
#| tbl-cap: "Summary statistics for the four different observation groups: public and 0% of the card deck is incentivized, public and 50% of the card deck is incentivized where the student is not incentivized, public and 50% of the card deck is incentivized where the student is incentivized, and public and 100% of the card deck is incentivized"

@@

# Create a bar plot
ggplot(food_choices, aes(x = as.factor(grade), fill = Switched)) +
  geom_bar(position = "dodge") +
  geom_text(
    aes(label = after_stat(count)),
    stat = "count",
    position = position_dodge(width = 0.9),
    vjust = -0.5, # Adjust the vertical position of the labels
    color = "black",
    size = 3
  ) +
  labs(x = "Grade",
       y = "Number of Observations") +
  scale_fill_manual(values = c("Cookie to Grape" = '#BDBDBD',"Grape to Cookie" = '#757575', "Not Changed" = '#424242')) +
  scale_x_discrete(breaks = as.character(0:8)) +
  theme_minimal()

@@

# Create the bar graph
ggplot(proportions, aes(x = factor(free), y = Proportion, fill = factor(free))) +
  geom_bar(stat = "identity") +
  labs(x = "Eligible for Free Lunch",
       y = "Proportion",
       fill = "Eligible for Free Lunch") +
  scale_fill_manual(values = c('#BDBDBD', '#424242'), labels = c("No", "Yes")) +
  scale_x_discrete(labels = c("0" = "No", "1" = "Yes")) +  # Adjust x-axis labels  
  scale_y_continuous(limits = c(0, 1)) +  # Set y-axis limits  
  theme_minimal()

@@

# Create the bar chart
ggplot(proportions_long, aes(x = grade, y = proportion, fill = choice)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Grade",
       y = "Proportion",
       fill = "Choice") +
  scale_fill_manual(values = c("grapes_proportion" = '#BDBDBD', "cookies_proportion" = '#424242'),
                    labels = c("Grapes", "Cookies")) +
  ylim(0,1) +
  theme_minimal()

@@

# Create the bar chart
ggplot(proportions_long, aes(x = male, y = proportion, fill = choice)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Gender",
       y = "Proportion",
       fill = "Choice") +
  scale_fill_manual(values = c("grapes_proportion" = '#BDBDBD', "cookies_proportion" = '#424242'),
                    labels = c("Grapes", "Cookies")) +
  ylim(0,1) +
  theme_minimal()
